Plant-pollintor networks worldwide are composed by the same specific building

### 2021-07-20 Draft/Draft.Rmd
Edits on the first 2 paragraphs

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

Ecological processes leave distinct structural imprints on species interactions shaping  the topology of mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or the higher number of pollinator species than plant species [@bluthgen2007]. In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020]. However, both species level information or an holistic view of the full network involves missing relevant information for the understanding of ecological processes [@simmons2019].

Indirect interactions (i.e., motifs), commonly referred as the building blocks that depict subsets of interactions of the network [@milo2002], are a widespread phenomenon in ecological communities [@strauss1991]. For instance, plant species can facilitate or compete for pollinator's visitation when two species are visited by the same pollinator [@ghazoul2006]. Despite the relevance of indirect interactions in ecological communities, plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. The study of @simmons2020 have shown that the different processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions. However, we still ignore which are the general patterns observed in the distribution of plant-pollinator motifs worldwide.

>>>>

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: true
bibliography: bibliography.bib
---

@@

Ecological processes leave distinct structural imprints on species interactions shaping the topology of mutualistic networks. Detecting those relationships is not trivial since they go beyond pair-wise interactions, but may get blurred when considering full network descriptors. However, recent work has shown the network meso-scale can capture this important information. The meso-scale describes network subgraphs representing patterns of interactions between a small number of species (i.e. motifs) and those constitute the building blocks of the whole network. Here, we have compiled 60 networks from 18 different studies and show that some motifs are consitently over-represented worldwide, suggesting that the building blocks of plant-pollintor networks are not random and are associated to ... Second, we show that the position of pollinator guilds and plant reproductive strategies is not random with respect to the positions occupied within each motif. ... Hence, we show that species ecology is shaping the building blocks that conform the web of life.

@@

The interaction between plants and pollinators can be studied at different scales, from species level interactions (micro-scale) to the full network structure (macro-scale). Research of the plant-pollinator network structure have proven common invariant structural properties across them including a degree distribution that decays as a power law [@jordano1987], nestedness [@bascompte2003], or modularity in large networks [@olesen2007]. In addition, species phenological overlap, morphological matching and species abundances have been shown to be determinant for the understanding of pairwise plant-pollinator interactions [@bartomeus2016; @stang2006; @peralta2020]. However, both species level information and the holistic view of the full network involves missing relevant information for the understanding of ecological processes [@cirtwill2018; @simmons2019].

Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008]. Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research allows to consider both direct and indirect interactions [@simmons2019]. Motifs are commonly referred to as the building blocks of a network that depict subsets of interactions or subnetworks [@milo2002]. Motif analysis in plant-pollinator networks (meso-scale) have shown that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020]. Despite this recent progress in the understanding of ecological processes that shape indirect interactions in plant-pollinator networks, global patterns of indirect interactions (over- and under- representation of motifs) are still unknown.
